\documentclass[12pt]{article}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=black, citecolor=black, urlcolor=black}

\begin{document}
\thispagestyle{empty}

\begin{center}
{\LARGE \textbf{Patent Portfolio Scale, Relatedness, and Institutional Evaluation}}
\end{center}

\vspace{1cm}

\noindent \textbf{Author:} Koki Arai

\noindent \textbf{Affiliation:} Faculty of Business Studies, Kyoritsu Women's University, Tokyo, Japan

\noindent \textbf{Corresponding author email:} koki.arai@nifty.ne.jp

\vspace{0.5cm}

\noindent \textbf{Keywords:} patent portfolio; path dependence; local search; patent examination; technological relatedness

\noindent \textbf{JEL classification:} O31, O32, O34, L65

\vspace{1cm}
\hrule
\vspace{0.5cm}

\section*{Statements and Declarations}

\noindent \textbf{Funding:} This work was supported by JSPS KAKENHI Grant Number 23K01404.

\vspace{0.3cm}
\noindent \textbf{Conflict of Interest / Competing Interests:} The author declares no conflict of interest.

\vspace{0.3cm}
\noindent \textbf{Ethics Approval:} Not applicable. This study uses firm-level administrative patent data licensed from the Institute of Intellectual Property (Tokyo) and does not involve human or animal subjects.

\vspace{0.3cm}
\noindent \textbf{Consent to Participate / Consent for Publication:} Not applicable.

\vspace{0.3cm}
\noindent \textbf{Data Availability Statement:} The raw IIP Patent Database cannot be redistributed by the author under its licensing terms. Replication code, variable-construction scripts, and non-confidential derived outputs sufficient to reproduce the reported estimates for researchers with independent access to the database will be made publicly available at a repository (\url{https://github.com/Koki-Arai}) upon acceptance.

\vspace{0.3cm}
\noindent \textbf{Code Availability:} Analysis code (Python; PPML via pyfixest, survival models via lifelines) will be made available at the repository referenced above upon acceptance.

\vspace{0.3cm}
\noindent \textbf{Author Contribution:} K.A. is the sole author and is responsible for all aspects of the conceptualization, data curation, formal analysis, and writing of this manuscript.

\vspace{0.3cm}
\noindent \textbf{Acknowledgements:} The author thanks Keita Kinjo and other Faculty colleagues for helpful comments on earlier stages of this research. All remaining errors are the author's own.

\vspace{0.3cm}
\noindent \textbf{ORCID:} 0000-0002-6907-4046

\end{document}
